Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-06 Cover_letter_JPM.tex
submission

%%% for abbreviations, or acronyms
\usepackage[acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{ncbi}{NCBI}{National Center for Biotechnology Information}
\newacronym{degs}{DEGs}{differentially expressed genes}

\newacronym{fdr}{FDR}{false discovery rate}
\newacronym{hpa}{HPA}{the Human Protein Atlas}
\newacronym{hnscc}{HNSCC}{head and neck squamous cell carcinoma}
\newacronym{tcga}{TCGA}{the Cancer Genome Atlas}
\newacronym{tcpa}{TCPA}{the Cancer Proteome Atlas}
\newacronym{rna}{RNA}{ribonucleic acid}
\newacronym{rnaseq}{RNA-Seq}{RNA sequencing}
\newacronym{lncrna}{lncRNA}{long non-coding RNA}
%\newacronym{km}{KM}{Kaplan-Meier}
\newacronym{rppa}{RPPAs}{reverse-phase protein arrays}
\newacronym{rpma}{RPMA}{reverse-phase protein lysate microarray}

@@

July 05, 2021

@@

%According to the editor's comments, we have the manuscript checked for English grammar. %
We wish our revised manuscript could be satisfied and accepted for publication in Journal of Personalized Medicine. 
Thank you very much for the kind helps and the reviewers' critical comments.\\[0.3cm]

@@

After morning meditation in a wonderful day of February 2021,, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We briefed this section (and Figure 6), then will submit rest of it in the other manuscript.

@@

% **** [2021/06/22] by Bayes_survival.R
% k-fold Cross-validation
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
%#Calculating Cox p-value...Done [2021/06/22] 19:42
%#Performing directed random walk...Done
%#Performing cv.glmnet...Done
%#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
%cv.mod.candidate has 62 genes 
The results shows that the model-selected features (62 genes) distribute within the region of small effect size (HR) on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}), if see them individually.

@@

% Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
%the left vertical line in the plot shows us where the cross-validation error curve hits its minimum.
%The final gene signature has been selected, including 4 genes, named HK1, EZR, RRAGA, and DUSP16 .; fentastic4
% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
LASSO calculate the (non-zero) coefficients of features, while the 62 genes hit the minimum of cross-validation error.
% in lambda 1se
%cv.mod$glmnetRes$lambda.1se
We further limited gene selection (13 out of 62) by the most regularized model under cross-validation error within 1 standard deviation of the minimum.
According to their \textit{P} values (please see Table \ref{tab:signature4}), 
we found a gene signature, HK1, EZR, RRAGA, and DUSP16 to predict their survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1.0 on the volcano plot of TCGA HNSCC.

@@

\begin{figure}[ht]
%    \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=6cm]{rplot_KMplot_HK1.pdf}
    \caption{Kaplan-Meier plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
    \caption{Volcano plot}
  \end{subfigure}
%However, # 4 gene signature: #### 
%# "EZR" has \textit{P} value $>0.05$
  \caption{(a) Overall survival in TCGA HNSCC for a gene signature including HK1, EZR, RRAGA, and DUSP16 (Kaplan-Meier \textit{P} value = \num{1.31e-6}); (b) Those genes (listed on the right side) have not significant hazard ratio (HR) if calculated individually (EZR is not shown on volcano plot due to it's Kaplan-Meier \textit{P} value $>0.05$)}
    \label{fig:signature4}
\end{figure}

@@

%Workflow of GDCRNATool
% reference https://www.biostars.org/p/153013/
%Tutorial: Survival analysis of TCGA patients
%integrating gene expression (RNASeq) data.
%Why would you want to do survival analysis based on gene expression data? Well, let's say you
% **** DEGs is a different concept with cutoff finding survival analysis of individual gene expression
They have several genes that are differentially expressed between tumor and normal samples.

@@

%%% https://www.biostars.org/p/153013/
%% download data with offline analysis
%Usually, investigators could download the TCGA data in order to analyze and find expression biomarkers.
% https://groups.google.com/forum/m/#!msg/ucsc-cancer-genomics-browser/YvKnWZSsw1Q/3IAkkEMyFa4J
% from Mary Goldman and Jing Zhu, UCSC Cancer Browser
% https://genome-cancer.ucsc.edu/
%Here are the summarized techniques currently used: from 2000 to 2017\cite{Tonella2017a}
%Gene expression profiling is applied for HNSCC to help in early diagnosis, prediction of recurrence or metastasis, prediction of prognosis or response to some therapies.

@@

Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019}\cite{Xu2021a} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
Gene expression data was downloaded from the TCGA or Gene Expression Omnibus (GEO) database (e.x. GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).

@@

%e.x. GSE30784: 167 HNSCC samples and 45 normal controls). 
They employed the Database for Annotation, Visualization, and Integrated Discovery (DAVID, available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function. 
The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions.

@@

The candidate genes were validated via the Gene Expression Profiling Interactive Analysis tool (GEPIA1/2 database using TCGA datasets, developed by Zefang Tang and his colleagues\cite{Tang2017a}\cite{Tang2019}

@@

), GEPIA2021\cite{Li2021} (available at http://\\gepia2021.cancer-pku.cn/), or the Human Protein Atlas (HPA) website.

@@

Finally, the gene expression profile from the GEO and HNSCC cell lines and tissues were used to verify these biomarkers.

@@

% 不要誇大說明 謙虛道歉
We apologize for exaggerating the difficulties of our workflow.
% ok
The paragraphs marked in \textcolor{red}{Red} on page 11 (line 286) to page 12 (line 314) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.

\begin{MyIndent}
\begin{MyColorPar}{red}
%%%
"
There are two essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.

First, since \acrshort{tcga} genomics data were harmonized, 
% three things were found during our investigating and data cleaning:
the pre-processing of TCGA RNA-Seq in our workflow has been done as follows: 
\begin{outline}
\1 HNSCC samples without complete clinical information have been removed;
\1 Null expressed genes in more than 30\% of the HNSCC samples have been excluded; % or 50\%
\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.
\end{outline}
After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that expression value of two genes (gene ID: 9906 and gene ID: 728661) was saved together under the entity of gene symbol "SLC35E2".
The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
% http://gepia2.cancer-pku.cn/#survival is SLC35E2; 證明 TCGA has error
% [line 1549]
%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
%[line 1654]
%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
%NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
According to the Human Gene Database (available at https://www.genecards.org/Search/Keyword?\\queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and SLC35E2B (Gene ID: 728661) should be the correct entities for the TCGA HNSCC dataset.
% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
% keyword: (SLC35E2) AND "Homo sapiens" 
SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\\\#!/hgnc\_id/HGNC:20863).
Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in this TCGA HNSCC dataset from 20499 to 20500.
% updated on 18-May-2021 then 01 July 2021

@@

% dissection
%ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
Second, we analyzed the error log during the cutoff finding and Cox modeling, 
the result shows that program running could be halted by several technical problems.
These include:
\begin{outline}

\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression;
\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate;
%1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
%Error in survdiff.fit(y, groups, strata.keep, rho) : at A1CF
% error at 16115 gene ""; why? 518 values all are -0.04203 at T
%  There is only 1 group 
%This is because of skewed distribution of the expression value. 
% 67/518 =  13% cases >1, while 450 (87%) cases = -0.30949; so median is -0.30949; 
% all cases belong to >= median => 改為 > median 即可
% 2) % survfit 16114 has data set has no non-missing observations: NA's 113/518 cases
% median = NaN :-); 
% solved by cutoff <- median(gset_OS_mRNA2[, i], na.rm = TRUE)
% and NaN imputation as median
\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow).
\end{outline}
These technical problems could not be detected prior to program running.
It might be due to skewed distribution of the expression value or even random error derived during the RNA sequencing procedure. % heterogeneity
"

>>>>

%%% for abbreviations, or acronyms
\usepackage[acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{ncbi}{NCBI}{National Center for Biotechnology Information}
\newacronym{degs}{DEGs}{differentially expressed genes}
\newacronym{ihc}{IHC}{immunohistochemistry}
\newacronym{fdr}{FDR}{false discovery rate}
\newacronym{hpa}{HPA}{the Human Protein Atlas}
\newacronym{hnscc}{HNSCC}{head and neck squamous cell carcinoma}
\newacronym{tcga}{TCGA}{the Cancer Genome Atlas}
\newacronym{tcpa}{TCPA}{the Cancer Proteome Atlas}
\newacronym{rna}{RNA}{ribonucleic acid}
\newacronym{rnaseq}{RNA-Seq}{RNA sequencing}
\newacronym{lncrna}{lncRNA}{long non-coding RNA}
%\newacronym{km}{KM}{Kaplan-Meier}
\newacronym{rppa}{RPPAs}{reverse-phase protein arrays}
\newacronym{rpma}{RPMA}{reverse-phase protein lysate microarray}

@@

July 06, 2021

@@

%According to the editor's comments, we have the manuscript checked for English grammar. %
We wish our revised manuscript could be satisfied and accepted for publication in Journal of Personalized Medicine.
We are updating very much from this major revision.
Thank you very much for the kind helps and the reviewers' critical comments.\\[0.3cm]

@@

After morning meditation in a wonderful day of February 2021, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi wants to express that "stress should also be a kind of biomarker, which includes into the HNSCC study in the future".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We briefed this section (and Figure 6), then will submit rest of it in the other manuscript (study of electronic health record in survival analysis).

@@

% **** [2021/06/22] by Bayes_survival.R
% k-fold Cross-validation
%[line 403] cv.mod <- cvRLassoCox(x=x.train, y=y.train, globalGraph=dGMMirGraph, nfolds = 10) 
%#Calculating Cox p-value...Done [2021/06/22] 19:42
%#Performing directed random walk...Done
%#Performing cv.glmnet...Done
%#code inside: fit.lasso <- cv.glmnet(x.train, y.train, family="gaussian", alpha=1) # L1-regularization, LASSO
%Rplot_GSE65858_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
% Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_Bayes62_FDRKM.pdf
%cv.mod.candidate has 62 genes
% lasso 就是要找出 coefficient of regression non-zero 的基因: selected features
LASSO calculate the (non-zero) coefficients of features to hit the minimum of cross-validation error.
The results shows that the model-selected features (62 genes) distribute within the region of small effect size (HR from 0.6 to 1.7) on our previous volcano plots (please see Figure \ref{fig:Bayes62}; comparing with Figure \ref{fig:hazards3} and Figure \ref{fig:hazards534}), if see them individually.

@@

% Y-axis of the cross-validation error curve (red dotted line) (partial likelihood deviance)
%the left vertical line in the plot shows us where the cross-validation error curve hits its minimum.
%The final gene signature has been selected, including 4 genes, named HK1, EZR, RRAGA, and DUSP16 .; fentastic4
% in lambda 1se
%cv.mod$glmnetRes$lambda.1se
We further limited gene selection (13 out of 62) by the most regularized model under cross-validation error within 1 standard deviation of the minimum.
According to their \textit{P} values (please see Table \ref{tab:signature4}), 
we found a gene signature, HK1, EZR, RRAGA, and DUSP16, which will has survival impact on TCGA HNSCC cohort (please see Figure \ref{fig:signature4}).
DUSP16 has negative coefficient in the LASSO regression model, compatible with HR less than 1.0 on the volcano plot of TCGA HNSCC.

@@

\begin{figure}[ht]
%    \centering
  \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[width=6cm]{rplot_KMplot_HK1.pdf}
    \caption{Kaplan-Meier plot}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.5\textwidth}
    \includegraphics[width=8cm]{Rplot_TCGA_HNSCC_CoxHR_CAMK2N1_signature4_FDRKM.pdf}  
    \caption{Volcano plot}
  \end{subfigure}
%However, # 4 gene signature: #### 
%# "EZR" has \textit{P} value $>0.05$
  \caption{The LASSO-Cox regression model predict a set of gene signature. (a) Overall survival in TCGA HNSCC for the gene signature including HK1, EZR, RRAGA, and DUSP16 (Kaplan-Meier \textit{P} value = \num{1.31e-6}); (b) HK1, RRAGA, and DUSP16 have small effect size---hazard ratio within 0.6-1.7, if calculated individually. And EZR has Kaplan-Meier \textit{P} value $>0.05$. (\textcolor{red}{Red}-squared genes are the biomarker candidates found by sliding-window cutoff survival analysis)}
    \label{fig:signature4}
\end{figure}
%(listed on the right side)

@@

%They have several genes that are differentially expressed---\acrfull{degs} between tumor and normal samples.

@@

@@

Some researchers\cite{Loraine2015a}\cite{Tonella2017a}\cite{Zhao2018}\cite{Li2018a}\\\cite{Huang2019}\cite{Shen2019}\cite{Schmitt2019} tried to find \acrfull{degs} of the HNSCC samples at both genotypic and phenotypic levels (without survival information) for biomarker discovery.
Gene expression data were downloaded from the TCGA or Gene Expression Omnibus (GEO) databases (e.g., GSE117973\cite{Schmitt2019}, HIPO-HNC cohort has n = 87).

@@

%e.g., GSE30784: 167 HNSCC samples and 45 normal controls). 
They used the Database for Annotation, Visualization, and Integrated Discovery---DAVID (available at https://david.ncifcrf.gov/) to obtain information for Gene Ontology (GO), including biological processes, the cellular component, and molecular function. 
The Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway analysis was also used to annotate the potential functions of their biomarker candidates.

@@

They validated the candidate genes by using the web-based tools of Gene Expression Profiling Interactive Analysis tool---GEPIA and Human protein atlas (HPA) databases.
GEPIA was developed, using TCGA datasets, by Zefang Tang and his colleagues (version 1\cite{Tang2017a}, version 2\cite{Tang2019}, and GEPIA2021\cite{Li2021}, available at http://gepia2021.cancer-pku.cn/).

@@

HPA\cite{Uhlen2017} applied \acrfull{ihc} for the TCGA database (please see details in the Discussions section "Validation by Web-based Tools").

@@

Finally, their biomarkers were verified by using the gene expression profile from the GEO, HNSCC cell lines and tissues.\\

@@

% 不要誇大說明 謙虛道歉
We apologize for exaggerating the difficulties in our work.
% ok
The paragraphs marked in \textcolor{red}{Red} on page 11 (line 286) to page 12 (line 314) are the part of the manuscript that has been revised. 
We want to share the experience for this HNSCC data pre-processes in detail to help further survival analysis in other TCGA cohorts.
We added a paragraph of "Technical Consideration".
Also, it is shown here in the following two paragraphs.\\
We are improving very much from this major revision.
Thanks for the reviewers' kind help again.

\begin{MyIndent}
\begin{MyColorPar}{red}
%%%
"
3.3 Technical Consideration\\[0.2cm]
There are two essential points of biomarker discovery from survival analysis of the TCGA HNSCC dataset.

First, since \acrshort{tcga} genomics data were harmonized, 
% three things were found during our investigating and data cleaning:
the pre-processing of TCGA RNA-Seq in our workflow has been done as follows: 
\begin{outline}
\1 HNSCC samples without complete clinical information have been removed;
\1 Null expressed genes in more than 30\% of the HNSCC samples have been excluded; % or 50\%
\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.
\end{outline}
After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that expression value of two genes (gene ID: 9906 and gene ID: 728661) was saved together under the entity of gene symbol "SLC35E2".
The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
% http://gepia2.cancer-pku.cn/#survival is SLC35E2; 證明 TCGA has error
% [line 1549]
%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
%[line 1654]
%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
%NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
According to the Human Gene Database (available at https://www.genecards.org/Search/Keyword?queryString=\\SLC35E2), SLC35E2A (Gene ID: 9906) and SLC35E2B (Gene ID: 728661) should be the correct entities for the TCGA HNSCC dataset.
% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
% keyword: (SLC35E2) AND "Homo sapiens" 
SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!/\\hgnc\_id/HGNC:20863).
Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B and updated the number of protein-coding genes in this TCGA HNSCC dataset from 20499 to 20500.
% updated on 18-May-2021 then 01 July 2021

@@

% dissection
%ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
Second, we analyzed the error log during the cutoff finding and Cox modeling, 
the result shows that program running could be halted under several technical situation.
These include:
\begin{outline}

\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression (coxph), due to zero in M (distant metastasis) patient subgroup;
\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate;
%1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
%Error in survdiff.fit(y, groups, strata.keep, rho) : at A1CF
% error at 16115 gene ""; why? 518 values all are -0.04203 at T
%  There is only 1 group 
%This is because of skewed distribution of the expression value. 
% 67/518 =  13% cases >1, while 450 (87%) cases = -0.30949; so median is -0.30949; 
% all cases belong to >= median => 改為 > median 即可
% 2) % survfit 16114 has data set has no non-missing observations: NA's 113/518 cases
% median = NaN :-); 
% solved by cutoff <- median(gset_OS_mRNA2[, i], na.rm = TRUE)
% and NaN imputation as median
\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow).
\end{outline}
These technical problems could not be detected prior to program running.
It might be due to skewed distribution of the expression value or even random error derived during the RNA sequencing procedure. % heterogeneity
"

### 2021-07-06 main.tex
submission

They validated the candidate genes by using the web-based Tools of Gene Expression Profiling Interactive Analysis tool---GEPIA and Human protein atlas (HPA) databases.

@@

% dissection
%ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
Second, we analyzed the error log during the cutoff finding and Cox modeling, 
the result shows that program running could be halted by several technical problems.
These include:
\begin{outline}

\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression;
\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate;
%1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
%Error in survdiff.fit(y, groups, strata.keep, rho) : at A1CF
% error at 16115 gene ""; why? 518 values all are -0.04203 at T
%  There is only 1 group 
%This is because of skewed distribution of the expression value. 
% 67/518 =  13% cases >1, while 450 (87%) cases = -0.30949; so median is -0.30949; 
% all cases belong to >= median => 改為 > median 即可
% 2) % survfit 16114 has data set has no non-missing observations: NA's 113/518 cases
% median = NaN :-); 
% solved by cutoff <- median(gset_OS_mRNA2[, i], na.rm = TRUE)
% and NaN imputation as median
\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow).
\end{outline}
These technical problems could not be detected prior to program running.
It might be due to skewed distribution of the expression value or even random error derived during the RNA sequencing procedure. % heterogeneity

>>>>

They validated the candidate genes by using the web-based tools of Gene Expression Profiling Interactive Analysis tool---GEPIA and Human protein atlas (HPA) databases.

@@

% dissection
%ZSWIM2\_archive.Rda % 其實最困難的在於 unknown error (ZSWIM2) 
Second, we analyzed the error log during the cutoff finding and Cox modeling, 
the result shows that program running could be halted under several technical situation.
These include:
\begin{outline}

\1 32.2\% event has "one group" issue in confusion matrix of Chi-square test in Cox regression (coxph), due to zero in M (distant metastasis) patient subgroup;
\1 21.05\% error occurs by "one group" issue in log-rank test (survdiff or survdiff.fit function in R package "survival") in Kaplan-Meier estimate;
%1) ok [1] "[ 4 / 20083 ] Generating median-cut KM plot of A1BG"
%Error in survdiff.fit(y, groups, strata.keep, rho) : at A1CF
% error at 16115 gene ""; why? 518 values all are -0.04203 at T
%  There is only 1 group 
%This is because of skewed distribution of the expression value. 
% 67/518 =  13% cases >1, while 450 (87%) cases = -0.30949; so median is -0.30949; 
% all cases belong to >= median => 改為 > median 即可
% 2) % survfit 16114 has data set has no non-missing observations: NA's 113/518 cases
% median = NaN :-); 
% solved by cutoff <- median(gset_OS_mRNA2[, i], na.rm = TRUE)
% and NaN imputation as median
\1 0.78\% has unknown reason (so those 159 genes has been excluded in our workflow).
\end{outline}
These technical problems could not be detected prior to program running.
It might be due to skewed distribution of the expression value or even random error derived during the RNA sequencing procedure. % heterogeneity
